SparseIDS: Learning Packet Sampling with Reinforcement Learning

### 2020-02-03 paper_rl/paper.tex
Changes

@@

So far, we have always trained \ours{} with a fixed tradeoff parameter $\alpha$. Nevertheless, there is also an important use case in which an operator wants a certain minimum sparsity, for example 50\%, to limit the necessary computation power and thus reduce costs. 
We thus propose a method that enables steering the tradeoff to achieve a certain desired sparsity.
\begin{enumerate}
\item A model is trained where the tradeoff is randomly chosen for each flow during training. We set the probability distribution to be a uniform distribution between 0 and 1. We add a new feature to each packet which indicates the tradeoff chosen for this flow so that it can adapt its sampling strategy in anticipation of the tradeoff that will determine the reward.
\item During deployment, the tradeoff is set to the maximum that was used during training (1 in our case), which results in maximum sparsity. Then, the tradeoff is continuously incremented if the current sparsity is still under the specified minimum. It is important that the tradeoff can never fall below 0 since this is a case that was not encountered during training and which can lead to anomalous behavior. 
\end{enumerate}

%{{"../plots/plot/flows_pred_plots2_outcomes_0_3.pickle_5_DoS - DDoS-DoS Hulk"}
\begin{figure}
\centering
  \includegraphics[width=\columnwidth]{{"img/lstm_module_8.pth_global_tradeoff_1.0_steering_step_size_0.05_steering_target_sparsity_0.5_batches_to_consider_for_steering_500_sampling_rl"}.pdf}
  \caption{Steering the tradeoff with an allowed minimum sparsity of 50\%. The tradeoff is initialized as 1 in the beginning and continuously lowered as long as the sparsity is higher than 50\% for CIC-IDS-2017. The procedure stops if the minimum sparsity is reached or the tradeoff reached its minimum of 0, which is the case here. Sparsity falls from around 74.5\% to 73.5\%.}
  \label{fig:steering}
\end{figure}

>>>>

\begin{figure}
\centering
  \includegraphics[width=\columnwidth]{{"img/events.out.tfevents.1579352256.gpu"}.pdf}
  \caption{Training with a tradeoff of 0.1 with continuous actions for the CIC-IDS-2017 dataset. Training accuracy increases sharply in the beginning while becoming slower the longer training lasts. Sparsity increases sharply in the beginning and then slower. As the classifier gets better, the \gls{rl} starts skipping more packets.}
  \label{fig:training}
\end{figure}

@@

So far, we have always trained \ours{} with a fixed tradeoff parameter $\alpha$. Nevertheless, there is also an important use case in which an operator wants a certain minimum sparsity, for example 50\%, to limit the necessary computation power and thus reduce costs. 
We thus propose a method that enables steering the tradeoff to achieve a certain desired sparsity.
\begin{enumerate}
\item A model is trained where the tradeoff is randomly chosen for each flow during training. We set the probability distribution to be a uniform distribution between 0 and 1. We add a new feature to each packet which indicates the tradeoff chosen for this flow so that it can adapt its sampling strategy in anticipation of the tradeoff that will determine the reward.
\item During deployment, the tradeoff is set to the maximum that was used during training (1 in our case), which results in maximum sparsity. Then, the tradeoff is continuously decremented if the current sparsity is still under the specified minimum. It is important that the tradeoff can never fall below 0 since this is a case that was not encountered during training and which can lead to anomalous behavior. 
\end{enumerate}

\begin{figure}
\centering
  \includegraphics[width=\columnwidth]{{"img/lstm_module_8.pth_global_tradeoff_1.0_steering_step_size_0.05_steering_target_sparsity_0.5_batches_to_consider_for_steering_500_sampling_rl"}.pdf}
  \caption{Steering the tradeoff with an allowed minimum sparsity of 50\%. The tradeoff is initialized as 1 in the beginning and continuously lowered as long as the sparsity is higher than 50\% for CIC-IDS-2017. The procedure stops if the minimum sparsity is reached or the tradeoff reached its minimum of 0, which is the case here. Sparsity falls from around 74.5\% to 73.5\%.}
  \label{fig:steering}
\end{figure}
